Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-10 papers/marlowe2019/paper.tex
Conclusions and future work.

Because Marlowe is a DSL, we are able to build special purpose tools and techniques to support it. Crucially in a financial environment, we are able to \emph{exhaustively analyse contracts} without executing them, so that we can, for instance, check whether any particular contract is able to make all the payments it should: in the case it is not, we get an explicit example of how it can fail. This analysis, reported in Section \ref{sec:static}, is built into the Marlowe Playground. We are also able to use formal verification to prove properties of the implementation of Marlowe, including a guarantee that ``money in $=$ money out'' for all contracts; this is covered in Section~\ref{sec:verification}. 
% PLS: Should we divide the analysis/formalisation section in two? SJT: done

>>>>

Because Marlowe is a DSL, we are able to build special purpose tools and techniques to support it. Crucially, in a financial environment we are able to \emph{exhaustively analyse contracts} without executing them, so that we can, for instance, check whether any particular contract is able to make all the payments it should: in the case it is not, we get an explicit example of how it can fail. This analysis, reported in Section \ref{sec:static}, is built into the Marlowe Playground. We are also able to use formal verification to prove properties of the implementation of Marlowe, including a guarantee that ``money in $=$ money out'' for all contracts; this is covered in Section~\ref{sec:verification}. 
% PLS: Should we divide the analysis/formalisation section in two? SJT: done
